# A Minimal R Markdown Example

The contents of this document were adapted from one of
[Yihui Xie](https://yihui.name/)'s wonderful examples.

To convert to a HTML document, run this in R using the
`knitr::knit2html("knitr-markdown.Rmd")` command.

## Code chunks

Below are some code chunks as examples.

```{r named-chunk-1, results="asis"}
if (TRUE) cat("_hello_ **markdown**!", "\n")
```

Normally you do not need any chunk options.

```{r named-chunk-2, collapse=TRUE}
1+1
10:1
rnorm(5)^2
strsplit("hello, markdown vignettes", "")
```

Feel free to draw beautiful plots and write math $P(X>x)=\alpha/2$.

```{r}
n <- 300; set.seed(123)
x <- rnorm(n)
y <- rnorm(n)
```

```{r named-chunk-4}
par(mar = c(4, 4, 0.1, 0.1))
plot(x, y, pch = 21, cex = 5 * runif(n), col = "white", bg="gray")
```

You can use your own CSS file instead of the built-in style in the
**markdown** package -- just set the option `markdown.HTML.stylesheet`, e.g.

```{r named-chunk-5, eval=FALSE}
options(markdown.HTML.stylesheet = "path/to/a/custom/style.css")
```
