---
output:
  md_document:
    variant: markdown_github
---

# inlmisc

[![Travis Build Status](https://travis-ci.org/USGS-R/inlmisc.svg?branch=master)](https://travis-ci.org/USGS-R/inlmisc)
[![CRAN Version](https://www.r-pkg.org/badges/version/inlmisc)](https://CRAN.R-project.org/package=inlmisc)
[![CRAN Downloads](https://cranlogs.r-pkg.org/badges/inlmisc?color=brightgreen)](https://CRAN.R-project.org/package=inlmisc)
[![Dependencies](https://tinyverse.netlify.com/badge/inlmisc)](https://CRAN.R-project.org/package=inlmisc)
[![Coverage Status](https://coveralls.io/repos/github/USGS-R/inlmisc/badge.svg?branch=master)](https://coveralls.io/github/USGS-R/inlmisc?branch=master)
[![USGS Category](https://img.shields.io/badge/USGS-Support-yellow.svg)](https://owi.usgs.gov/R/packages.html#support)

## Description

The [R](https://www.r-project.org/) package **inlmisc** is a collection of functions for creating high-level graphics,
performing raster-based analysis, processing [MODFLOW](https://www.usgs.gov/mission-areas/water-resources/science/modflow-and-related-programs "USGS's modular hydrologic model")-based models,
selecting subsets using a genetic algorithm, creating interactive web maps, accessing color palettes, etc.
Used to support packages and scripts written by researchers at the U.S. Geological Survey (USGS)
Idaho National Laboratory (INL) [Project Office](https://www.usgs.gov/centers/id-water/science/idaho-national-laboratory-project-office "USGS INL Project Office").

## Installation

The current release is available on [CRAN](https://CRAN.R-project.org/package=inlmisc "The Comprehensive R Archive Network"),
which you can install using the following command:

```r
install.packages("inlmisc", dependencies = TRUE)
```

A recent version of [Pandoc](https://pandoc.org/installing.html) (>= 1.12.3)
is also required to run particular examples in the help documentation---[RStudio](https://rstudio.com/products/rstudio/)
includes this so you do not need to download Pandoc if working in a RStudio IDE.
The **webshot** package is imported from and has as a dependency the external program [PhantomJS](https://phantomjs.org/),
which may be installed using the command:

```r
webshot::webshotinstall_phantomjs()
```

For creating word clouds, the [OptiPNG](http://optipng.sourceforge.net/) program is recommended and needs to be accessible through the command window.
Finally, to install the development version of **inlmisc**, you need to clone the repository and build from source, or run:

```r
if (!requireNamespace("remotes")) install.packages("remotes")
remotes::install_github("USGS-R/inlmisc", dependencies = TRUE)
```

## Usage

Examples are given in the package help pages.
To access this documentation, run:

```r
library("inlmisc")
help(package = "inlmisc")
```

## Author

Jason C. Fisher (ORCID iD [0000-0001-9032-8912](http://orcid.org/0000-0001-9032-8912))

## Point of Contact

Jason C. Fisher (<jfisher@usgs.gov>)

## Suggested Citation

```{r "citation", echo=FALSE, results="asis"}
cit <- utils::citation(package="inlmisc")
print(cit, bibtex=FALSE)
```

## Contributing

We welcome your contributions and suggestions for how to make these materials more useful to the community. Please feel free to comment on the [issue tracker](https://github.com/USGS-R/inlmisc/issues) or open a [pull request](https://github.com/USGS-R/inlmisc/pull/new/master) to contribute.

```{r, echo=FALSE, results="asis"}
files <- c("CODE_OF_CONDUCT.md", "DISCLAIMER.md", "LICENSE.md")
for (f in files) cat(readLines(f), "\n\n", sep="\n")
```

## Support

The Idaho National Laboratory Project Office of the USGS supports the development and maintenance of **inlmisc**.
Resources are available primarily for maintenance and responding to user questions.
Priorities on the development of new features are determined by the inlmisc development team.

```{r "support", echo=FALSE, results="asis"}
cat(readLines("DISCLAIMER.md"), sep="\n")
```
