---
output:
  md_document:
    variant: markdown_github
---

inlmisc
=======

[![Travis Build Status](https://travis-ci.org/USGS-R/inlmisc.svg?branch=master)](https://travis-ci.org/USGS-R/inlmisc)
[![CRAN Version](https://www.r-pkg.org/badges/version/inlmisc)](https://CRAN.R-project.org/package=inlmisc)
[![CRAN Downloads](https://cranlogs.r-pkg.org/badges/inlmisc?color=brightgreen)](https://CRAN.R-project.org/package=inlmisc)
[![Dependencies](https://tinyverse.netlify.com/badge/inlmisc)](https://CRAN.R-project.org/package=inlmisc)
[![Coverage Status](https://coveralls.io/repos/github/USGS-R/inlmisc/badge.svg?branch=master)](https://coveralls.io/github/USGS-R/inlmisc?branch=master)
[![USGS Category](https://img.shields.io/badge/USGS-Support-yellow.svg)](https://owi.usgs.gov/R/packages.html#support)

Description
-----------

The [R](https://www.r-project.org/) package **inlmisc** is a collection of functions for creating high-level graphics,
performing raster-based analysis, processing [MODFLOW](https://www.usgs.gov/mission-areas/water-resources/science/modflow-and-related-programs "USGS's modular hydrologic model")-based models,
selecting subsets using a genetic algorithm, creating interactive web maps, accessing color palettes, etc.
Used to support packages and scripts written by researchers at the U.S. Geological Survey (USGS)
Idaho National Laboratory (INL) [Project Office](https://www.usgs.gov/centers/id-water/science/idaho-national-laboratory-project-office "USGS INL Project Office").

Installation
------------

The current release is available on [CRAN](https://CRAN.R-project.org/package=inlmisc "The Comprehensive R Archive Network"),
which you can install using the following command:

```r
install.packages("inlmisc", dependencies = TRUE)
```

To install the development version, you need to clone the repository and build from source, or run:

```r
if (!requireNamespace("remotes")) install.packages("remotes")
remotes::install_github("USGS-R/inlmisc", dependencies = TRUE)
```

Usage
-----

Examples are given in the package help pages.
To access this documentation, run:

```r
library("inlmisc")
help(package = "inlmisc")
```

Author
------

Jason C. Fisher (ORCID iD [0000-0001-9032-8912](http://orcid.org/0000-0001-9032-8912))

Suggested citation
------------------

```{r "citation", echo=FALSE, results="asis"}
cit <- utils::citation(package="inlmisc")
print(cit, bibtex=FALSE)
```

Contributing
------------

Please submit bug reports, suggestions, and pull requests to the
[issues tracker](https://github.com/USGS-R/inlmisc/issues).

Package support
---------------

The Idaho National Laboratory Project Office of the USGS supports the development and maintenance of inlmisc.
Resources are available primarily for maintenance and responding to user questions.
Priorities on the development of new features are determined by the inlmisc development team.

```{r "support", echo=FALSE, results="asis"}
cat(readLines("DISCLAIMER.md"), sep="\n")
```
